The problem and promise of scale in multilayer networks

### 2020-01-24 paper/manuscript.Rmd
move obs scale up

@@

#### Observational scale

Studies of social network analysis vary in the number and frequency of observations as well as the data collection technique used to generate networks (Davis et al. 2018; Webber and Vander Wal 2019).

>>>>

**Observational scale** (temorary header): Studies of social network analysis vary in the number and frequency of observations as well as the data collection technique used to generate networks (Davis et al. 2018; Webber and Vander Wal 2019).

@@
